% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experiences}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Currently}   {Course Instructor | GTA}{Mobile Application Development}{UNC Charlotte}
    {Sept, 2017} {
                      \begin{itemize}
                        \item Preparing course materials.
                        \item Instructing hands-on Android programming in-class.
                        \item Preparing assignments and designing the tasks.
                        \item Managing the logistics.                                                                   
                      \end{itemize}
                    }
                    {Android, GUI, Layouts, Lists, HTTP, APIs, SQLite, Firebase, Cloud Data and Storage, Maps and Geo}
  \emptySeparator
  \experience
    {Aug, 2017}   {Graduate Teaching Assistant}{Mobile Application Development}{UNC Charlotte}
    {Sept, 2016} {
                      \begin{itemize}
                        \item Coordinating other TAs as the lead TA.
                        \item Helping the student hands-on to make them understand the topics.
                        \item Helping the instructor to prepare assignments and design the tasks.
                        \item Grading.                                                                   
                      \end{itemize}
                    }
                    {Android, GUI, Layouts, Lists, HTTP, APIs, SQLite, Firebase, Cloud Data and Storage, Maps and Geo}
  \emptySeparator    
  \experience
    {Aug, 2016}   {Graduate Research Assistant}{CyberDNA Research Center}{UNC Charlotte}
    {Sept, 2015} {
                      \begin{itemize}
                        \item Applying data analytics methods to solve cyber threat problems.
                        \item Designing a framework for cyber threat hunt project.                                                                   
                      \end{itemize}
                    }
                    {Data analytics, R, Python, Visual Analytics}
  \emptySeparator
  \experience
    {Jul, 2015}   {Undergraduate Research Assistant}{Green Networking Research Group}{University of Dhaka}
    {Jan, 2012} {
                      \begin{itemize}
                        \item Working in a project named, "Driver Distraction Management Using Sensor Data Cloud"
                        \item Integrating location based services with cloud.
                        \item Building sensing hardware prototype with Raspberry PI.
                        \item Managing cloud server and database.                                                                    
                      \end{itemize}
                    }
                    {VPS, Raspberry PI, Google Cloud, Amazon AWS}
  \emptySeparator
\end{experiences}
