% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}
	\project
	{Exploring users' perceptions of being employed as user-beacons in the wild}{Currently working}
	{We are conducting an exploratory qualitative user study to deeply understand user perspectives on being users-as-beacons. We are exploring the overall comfort of being user-beacons, perceptions regarding interacting with other people around ads, privacy concerns, and what kind of controls and preferences they want to have in the system. We are also exploring the possibility of deploying this kind of system and creating a social web of consumer-generated advertising that reflects users privacy considerations.}
	{}
	{Qualitative, Interview, Inductive coding, BLE, Users as Beacons}
	\project
	{Exploring users' opinions of being employed as mobile advertisers}{Fall 2017}
	{We designed and ran a user study in the university’s bookstore, where we deployed our advertising system and explored users’ perceptions of being employed as user-beacons based on several key factors including perceptions of public exposure, the sensitivity of products, and peer influence.}
	{}
	{Role playing, Quantitative, Empirical study, Android, BLE, Consumer Generated Advertising}
	\project
	{Designing a cyber threat hunting game for the Cyber Security Symposium}{Spring 2017}
	{Cyber Threat Hunting is an emerging cyber security activity. Recent studies show that, although similar actions like threat hunting are being actively practiced in some organization, security administrator and policy makers are far from being satisfied with their effectiveness. Most security professionals lack expertise in data analytics while most people with data analytics skills lack security knowledge. To understand the necessity of threat hunting education at university level, we organized a \textit{Threat Hunting Competition} on campus with generated logs. We identified the skills needed for cyber threat hunting as well as the usage of logs to teach threat hunting at universities.}
	{}
	{Cyber Threat Hunting, Data Analytics}
\end{projects}