% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Publications}{\faLaptop}

\begin{itemize}
	\item $[$Honorable Mentions Award$]$ N. S. Miazi, C. A. C. Castro and M. Shehab, "Mobile Users as Advertisers: User Perceptions of Product Sensitivity, Exposure, and Public Influence," 2018 17th International Conference on Mobile and Ubiquitous Multimedia, Cairo, Egypt, 2018. (Not yet available in ACM library).
	\item M. N. S. Miazi, M. M. A. Pritom, M. Shehab, B. Chu and J. Wei, "The Design of Cyber Threat Hunting Games: A Case Study," 2017 26th International Conference on Computer Communication and Networks (ICCCN), Vancouver, BC, 2017, pp. 1-6.
	\item M. N. S. Miazi, Z. Erasmus, M. A. Razzaque, M. Zennaro and A. Bagula, "Enabling the Internet of Things in developing countries: Opportunities and challenges," 2016 5th International Conference on Informatics, Electronics and Vision (ICIEV), Dhaka, 2016, pp. 564-569.
	\item M. Tabassum, M. A. Razzaque, M. N. S. Miazi, and M. M. Hassan. 2016. "An Energy Aware Event-Driven Routing Protocol for Cognitive Radio Sensor Networks." Wireless Design \& Development. https://link.springer.com/article/10.1007/s11276-015-1043-8.
	\item M. N. S. Miazi, M. Tabassum, and M. A. Razzaque. 2015. “An Energy-Efficient Common Control Channel Selection Mechanism for Cognitive Radio Ad Hoc Networks.” Annals of. https://link.springer.com/article/10.1007/s12243-014.
\end{itemize}